saycam full dataset -- preprocessing

### 2020-01-31 paper/cogsci/paper_jan28.Rmd
figure edit + GD edits; same filenames

Beyond these early months, infants' motor and cognitive abilities mature, leading to a vastly different perspectives on the world. For example, crawlers see fewer faces and hands than do walking children [@Sanchez2018; @franchak2017see; @kretch2014] as well as different views of objects [@smith2011not]. Further, as infants learn to use their own hands to act on the world, they seem to focus on manual actions taken by their social partners, and their perspective starts to capture views of hands manipulating objects [@Fausey2016]. In turn, caregivers may also start to use their hands with more communicative intent, directing infants attention by pointing and gesturing to different events and objects during play [@yu2013joint].

@@

```{r examples, include = T, fig.env = "figure*", fig.pos = "h", fig.align='center', fig.width=8, fig.height=3.5, set.cap.width=T, num.cols.cap=2, fig.align = "center", fig.cap = "Example frames taken from the dataset, illustrating variability in the infant perspective across different locations. OpenPose detections are shown overlaid on these images (green dots = face, red dots = hands, orange dots = pose)."}
examples <- png::readPNG("figs/modifiedOPfigure_v3.png")
grid::grid.raster(examples)
```

@@

We also found an unexpectedly high proportion of hands in the view of infants, even when restricting the field of view to the upper 60% of the visual field of the videos.  One possibility is that these videos contain the viewpoints of children not only during structured interactions (e.g., play sessions at home or in the lab) but during everyday activities when children may be simply observing the actions of caregivers and other people in their environment. Further work that examines the variability in the social information in view across different activity contexts may help elucidate this new finding.

Indeed, a coarse analysis based the location the videos were filmed in already highlights the variability of the the social information in view, both across locations and between individual children. Even within a given, well-defined context---e.g., mealtime in kitchens---there was considerable variability: S saw more faces than A in the kitchen, and more faces in the kitchen than in other locations. This is likely because there are at least three ways to feed a young child in a kitchen: 1) sitting in front of the child, facing them as they sit in a high chair; 2) sitting behind the child, holding them as they face outward, and 3) sitting side by side. Each of these positions offer the child differing degrees of visual access to face and hands. Thus, even while the social information in view may be variable across children in different activitiy contexts, these analyses suggest they could be stable within children's typical experience.

@@

Nonetheless, we believe that these advances in datasets and methodologies represent a step in the right direction. The present paper demonstrates the feasibility of using a modern, off-the-shelf computer vision model to annotate the entirety of a very large dataset (here, >40M million frames) for the presence and size of people, hands, and faces, representing orders of magnitude more data relative to prior work [e.g., @Fausey2016]. We propose that the large-scale analysis of these kinds of dense datasets, collected with different fields of view, cameras and from many different laboratories, have the potential to create generalizable conclusions about the regularities of infant experience that scaffold learning.

>>>>

Beyond these early months, infants' motor and cognitive abilities mature, leading to a vastly different perspectives on the world. For example, crawlers see fewer faces and hands than do walking children [@sanchez2018postural; @franchak2017see; @kretch2014] as well as different views of objects [@smith2011not]. Further, as infants learn to use their own hands to act on the world, they seem to focus on manual actions taken by their social partners, and their perspective starts to capture views of hands manipulating objects [@Fausey2016]. In turn, caregivers may also start to use their hands with more communicative intent, directing infants attention by pointing and gesturing to different events and objects during play [@yu2013joint].

@@

```{r examples, include = T, fig.env = "figure*", fig.pos = "h", fig.align='center', fig.width=8, fig.height=3.5, set.cap.width=T, num.cols.cap=2, fig.align = "center", fig.cap = "Example frames taken from the dataset, illustrating variability in the infant perspective across different locations. OpenPose detections are shown overlaid on these images (green dots = face, red dots = hands, orange dots = pose)."}
examples <- png::readPNG("figs/modifiedOPfigure_v4.png")
grid::grid.raster(examples)
```

@@

We also found an unexpectedly high proportion of hands in the view of infants, even when restricting the field of view to the upper 60% of the visual field of the videos. Why might this be the case? One idea is that these videos contain the viewpoints of children not only during structured interactions (e.g., play sessions at home or in the lab) but during everyday activities when children may be playing by themselves or simply observing the actions of caregivers and other people in their environment. During these less structured times, caregivers may move about in the vicinity of the child but not interact with them as directly--leading to views where a person and their hands are visible from a distance, but this person's face may be turned away from the infant or occluded (see examples in Figure 1). Indeed, using the same pose detector on videos from in-lab play sessions, @sanchez2018postural found the opposite trend: slightly fewer hand detections than face detections from 8-16 months of age. Work that directly examines the variability in the social information in view across more vs. less structured activity contexts could further test this idea.

A coarse analysis based the location the videos were filmed in further highlights the variability of the social information in view during different activites, showing differences across locations and between individual children. Within a given, well-defined context---e.g., mealtime in kitchens---S saw more faces than A, and S  more faces in the kitchen than in other locations. This variability likely stems from the fact that thereare at least three ways to feed a young child: 1) sitting in front of the child, facing them as they sit in a high chair; 2) sitting behind the child, holding them as they face outward, and 3) sitting side by side. Each of these positions offer the child differing degrees of visual access to face and hands. While the social information in view may be variable across children in different activitiy contexts, these analyses suggest they could be stable within a given child's day-to-day experience.

@@

Nonetheless, we believe that these advances in datasets and methodologies represent a step in the right direction. The present paper demonstrates the feasibility of using a modern, off-the-shelf computer vision model to annotate the entirety of a very large dataset (here, >40M million frames) for the presence and size of people, hands, and faces, representing orders of magnitude more data relative to prior work. We propose that the large-scale analysis of these kinds of dense datasets, collected with different fields of view, cameras and from many different laboratories, have the potential to create generalizable conclusions about the regularities of infant experience that scaffold learning.

### 2020-01-31 preprocessing/preprocess_datasets.Rmd
figure edit + GD edits; same filenames

>>>>

```{r}
### Code to start to see if it maatters how many people are in the frame
age_info <- d_cropped %>%
  select(vid_name, frame, child_id, age_days)

one_person <- detections_cropped_SA %>%
  filter(num_people < 2) %>%
  left_join(d_cropped) %>%
  group_by(age_days, child_id) %>%
  summarize(prop_hands = mean(hand_detected), prop_faces = mean(face_detected))

wide_one_person <- one_person %>%
  gather(region, prop, prop_hands, prop_faces)

ggplot(wide_one_person, aes(x=age_days, y=prop, col=region)) +
  geom_point() +
  geom_smooth() +
  facet_grid(.~child_id) +
  ggtitle('hands vs faces (cropped) -- frames with only 1 person')
```
